### 2023-06-16 resilience.tex
up

{\bf Related problems.} 
A set of configurations $H$ is an {\em home space} for a set of configurations $X$ if every configuration reachable from $X$ can reach $H$. Resilience as introduced above essentially asks whether $\Safe$ is a home space for $\Bad$, whereas $k$-resilience and bounded-resilience focus more on the length of the paths from $\Bad$ to $\Safe$. The home space problem is decidable for
Petri nets when $X$ and $H$ are both semilinear sets~\cite{DBLP:journals/corr/abs-2207-02697}.
To these author's knowledge, there are no general results for home space in WSTS.

>>>>

{\bf Related problems.} 
A set of states $H$ is an {\em home space} for a set of states $X$ if every state reachable from $X$ can reach $H$. A {\em home space} is a state whose corresponding singleton set is a home space. Resilience as introduced above essentially asks whether $\Safe$ is a home space for $\Bad$, whereas $k$-resilience and bounded-resilience focus more on the length of the paths from $\Bad$ to $\Safe$. The home space problem is decidable for
Petri nets when $X$ and $H$ are both semilinear sets~\cite{DBLP:journals/corr/abs-2207-02697}.
To these author's knowledge, there are no general results for home space in WSTS.
